Calculating the Solvent Exposed Surface Area of Proteins with Intersecting Spheres

### 2020-06-07 Paper.tex
Changes

We also plotted the distribution of the SASA values for each calculator, and although they don't look too different in this example, more rigorous testing with a wider range of proteins has shown that \textsc{alphamol} gives far more accurate values than other algorithms, which is why it is incorporated into Rosetta today.
\begin{figure}
\caption{SASA Histograms for the Two Algorithms}
\centerline{\includegraphics[width=3in]{sasa}}
\end{figure}

>>>>

We also plotted the distribution of the SASA values for each calculator, and although they don't look too different in this example, more rigorous testing with a wider range of proteins has shown that \textsc{alphamol} gives far more accurate values than other algorithms, chiefly because of its consideration for internal cavities. This is why it is incorporated into Rosetta today.
\begin{figure}
\caption{SASA Histograms for the Two Algorithms}
\centerline{\includegraphics[width=3in]{sasa}}
\end{figure}
